%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Founder/Software Consultant} % Job title
    {Nomatic Software Consulting} % Organization
    {Portland, Oregon, USA} % Location
    {Jun. 2015 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborate with customer stakeholders to develop comprehensive software solutions that meet current and future business needs.}
        \item {Deployed and configured Airtable cloud spreadsheet--database platform for managing customer inquiries, project pipelines, and invoicing for a local food innovation center that supports Oregon's \$5 billion agriculture industry with B2B food research and support.}
      \end{cvitems}
    }
    
  \cventry
    {Graduate Research Assistant} % Job title
    {Oregon State University} % Organization
    {Corvallis, Oregon, USA} % Location
    {Sep. 2015 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architect and lead developer of a visuospatial source-code editor for managing human context in digital environments (built with Electron, Vite, React, Redux, and TypeScript).}
        \item {Developed interactive visualizations of Git repositories for human-centric version control.}
        \item {Built fully automated CI/CD pipelines on TravisCI, GitHub Actions, and Conveyor for cross-platform builds, packaging, and testing.}
        \item {Implemented unit-testing and an E2E (end-to-end) testing infrastructure in Cypress and Jest.}
        \item {Conducted empirical research into developer perceptions of software merge conflict processes, difficulties, and tools. Results received Best Paper Award at ICSME 2017.}
        \item {Conducted research into developer perceptions of CI practices and pitfalls. Results received Best Paper Award at ESEC/FSE 2017 and has 250+ citations.}
      \end{cvitems}
    }

  \cventry
    {Undergraduate Research Assistant} % Job title
    {} % Organization
    {} % Location
    {Mar. 2014 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conducted research on static analysis of Java/Kotlin code for automated refactoring of Android apps to inject dynamic permissions handling code that complies with Android 6.0's run-time permissions model.}
    	\item {Developed a Ruby on Rails web application for visualizing developer adherence to the TDD (Test-Driven Development) process.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Intern, PROSE} % Job title
    {Microsoft Corp.} % Organization
    {Seattle, Washington, USA} % Location
    {Feb. 2021 - Mar. 2021} % Date(s)
    {
   	  \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an interactive grid component plugin for JupyterLab interactive notebooks using Python, TypeScript, and CSS.}
        \item {Combined PBE (programming-by-example) and static type-inferencing techniques to create data analysis and formatting pipeline.}
        \item {Conducted qualitative HCI research into cognitive processes of recognizing ambient data in grid components.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Hewlett Packard Enterprise} % Organization
    {Corvallis, Oregon, USA} % Location
    {Jun. 2013 - Sep. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, proposed, and implemented warranty claims processing sub-system using Python and PHP to integrate into HP Web Press Dashboard web application.}
        \item {Implemented RESTful API service for ingesting printer consumables telemetry data from Inkjet High-Speed Product Solutions (IHPS) industrial printers for warranty claim validation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Analyst I} % Job title
    {Samaritan Health Services} % Organization
    {Corvallis, Oregon, USA} % Location
    {Apr. 2010 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided technical support for 85 enterprise software applications deployed at various regional healthcare facilities including Schlage Industrial Lock Control, MySQL, PostgreSQL, and Polycom Teleconference Systems.}
        \item {Held primary application support role for 30 enterprise applications, including 24/7 support during on-call rotations.}
      \end{cvitems}
    }
    
  \cventry
    {Help Desk Analyst} % Job title
    {} % Organization
    {} % Location
    {Jul. 2008 - Apr. 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided remote technical support for 7,000 healthcare employees at various regional healthcare facilities.}
        \item {Maintained a 99\% yearly customer satisfaction rating for two consecutive years.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Engineering Support Contractor} % Job title
    {Intel Corp.} % Organization
    {Hillsboro, Oregon, USA} % Location
    {May. 2007 - Jul. 2008} % Date(s)
    {
   	  \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a server deployment telemetry and provisioning application for enterprise-scale Linux/UNIX clusters using PHP and ColdFusion.}
        \item {Maintained operational and software security for 700 co-located Linux/UNIX servers across 5 global regions.}
        \item {Supported 6,000 production and test Linux/UNIX servers in use by electrical engineers and software developers.}
        \item {Developed SQL queries for automated weekly and monthly report generation of Linux/UNIX server cluster health analytics.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
