%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Ph.D. in Computer Science} % Degree
    {Oregon State University} % Institution
    {Corvallis, Oregon, USA} % Location
    {Sep. 2015 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Cumulative GPA: 3.57 / 4.00}
      	\item {Dissertation: \textit {Supporting Merge Comprehension when Resolving Merge Conflicts}}
        \item {Related Coursework: \textit {Data-Driven Software Engineering, Software Engineering Methods, Field Studies in SE \& HCI, Static Analysis \& Model Checking in SE, Programming Languages I \& II, Sensemaking in Software Development}}
    \item {Received Honorable Mention for Graduate Teaching 2018-2019.}
      \end{cvitems}
    }
    
    \cventry
    {B.S. in Computer Science} % Degree
    {Oregon State University} % Institution
    {Corvallis, Oregon, USA} % Location
    {Jan. 2012 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Cumulative GPA: 3.35 / 4.00}
      	\item {Minor: \textit {Business and Entrepreneurship}}
      	\item {Senior Project: \textit{Clang AST Analysis and Repair: A Code Quality and Compliance Development Tool}}
    	\item {Earned Honor Roll (GPA 3.5+) for four consecutive terms.}
      \end{cvitems}
    }

	\cventry
    {A.S. in Computer Information Systems} % Degree
    {Portland Community College} % Institution
    {Portland, Oregon, USA} % Location
    {Sep. 2007 - Dec. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Cumulative GPA: 3.34 / 4.00}
    	\item {Received President's Award (GPA 3.8+) and Dean's Award (GPA 3.5+) for three consecutive terms.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
