%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
\begin{briefSection}
Experienced full-stack software engineer with 13+ years across industry and academic environments.
Expert in developing and deploying scalable SaaS products using React, Node.js, TypeScript, and modern DevOps pipelines.
Founder of a consulting company delivering end-to-end solutions for SMBs.
Passionate about collaborating across teams, delivering scalable service solutions, and continuously improving development processes.
Strong self-starter and agile problem-solver with a PhD background in human-computer interaction and award-winning research contributions.  
\end{briefSection}

\begin{detailSection}
Founding Software Engineer at Nomatic Software Consulting which provides software consulting, development, and deployment for small and medium‑sized businesses in the US. Expansive technical skill set (13+ years in the software industry) with a strong focus on the React ecosystem, including React, React Hook Forms, Context API, and Redux. 
Experience managing complex form state, and developing modular, reusable components using Tailwind CSS.

Enthusiastic collaborator, partnering with UI/UX designers to translate prototypes into front‑end code and working with back‑end developers to integrate components with RESTful APIs, ensuring a smooth and consistent user experience. 
Researcher with cutting‑edge experience in software engineering and human‑computer interaction, having coauthored multiple award‑winning publications while completing a PhD graduate program. 
Autonomous and self‑driven individual able to solve issues with minimum supervision, while navigating uncertainty, complexity, and change within rapidly evolving environments. 
Love to contribute to open source communities and strive to provide mentorship to junior developers, collaboration with non‑technical roles, and foster diverse viewpoints in critical decision‑making processes.
\end{detailSection}

\end{cvparagraph}
